Turbulence in compact to giant HII regions

### 2021-12-17 strucfunc_paper.tex
Move turbulence section to discussion

\section{Methods}\label{sec:met}

@@

\begin{equation}\label{eq:functional}
B(r) = 2\sigma^2 \bigl( 1 - C(r) \bigr)
\end{equation}

Based on Equation \ref{eq:functional} we use the functional of the structure function in the form:
%
\begin{equation}\label{eq:ff}
b(r; r_0, m) = 2\sigma^2 \bigl( 1 - C(r) \bigr)
\end{equation}
%
where $C(r)$ is now the new form of the autocorrelation function in the proposed form:
%
\begin{equation}\label{eq:ffnew}
  C(r) = \exp \left[ -(\ln 2) \left( \frac{r}{r_0} \right)^m \right]
\end{equation}
%
substituting the previously $C(r)=1/[1+(r/r_{0})^{m}]$ \citep{1966igd..book.....K,1984ApJ...277..556S}.

@@

@@

Based on observations made with KPNO telescopes
\textit{complete KPNO acknowldgment}.
Based on observations made with ESO Telescopes at the La Silla Paranal Observatory under programme IDs 076.C-0888 and 098.D-0211.
Based on observations made as part of the Gaia-ESO Spectroscopic Survey
\textit{complete Gaia-ESO acknowldgment}.
Based on observations made with the WHT
\textit{complete WHT acknowldgment}.
JGV acknowledges and thanks CONACyT-Mexico for a PhD research scholarship.
We are grateful to Norberto Castro Rodríguez for providing maps of emission line velocity moments for 30 Doradus derived from MUSE-VLT observations.

>>>>

\section{Plane-of-sky velocity fluctuations}\label{sec:met}

@@

\begin{equation}\label{eq:functional}
B(r; r_0, m) = 2\sigma^2 \bigl( 1 - C(r) \bigr)
\end{equation}

%Based on Equation \ref{eq:functional} we use the functional of the structure function in the form:
%
%\begin{equation}\label{eq:ff}
%b(r; r_0, m) = 2\sigma^2 \bigl( 1 - C(r) \bigr)
%\end{equation}
%
%where  is now the new form of the correlation function in the form:
where $C(r)$ is a new form that we propose of the correlation function:
%
\begin{equation}\label{eq:ffnew}
  C(r) = \exp \left[ -(\ln 2) \left( \frac{r}{r_0} \right)^m \right]
\end{equation}
%
substituting the previously $C(r)=1/[1+(r/r_{0})^{m}]$ \citep{1966igd..book.....K,1984ApJ...277..556S}.

@@

\textit{Will 2021-12-10: Moving this section to later for now. Maybe
  this material could go in discussion}

@@

Based on observations made with KPNO telescopes
\textit{complete KPNO acknowledgment}.
Based on observations made with ESO Telescopes at the La Silla Paranal Observatory under programme IDs 076.C-0888 and 098.D-0211.
Based on observations made as part of the Gaia-ESO Spectroscopic Survey
\textit{complete Gaia-ESO acknowledgment}.
Based on observations made with the WHT
\textit{complete WHT acknowledgment}.
JGV acknowledges and thanks CONACyT-Mexico for a PhD research scholarship.
We are grateful to Norberto Castro Rodríguez for providing maps of emission line velocity moments for 30 Doradus derived from MUSE-VLT observations.
